Labeled object representation and manipulation with ITK

### 2007-08-29 article/Article.tex
some info about how is computed the roundness
darcs-hash:20070829134929-2fc9d-d02c527bfa0fcd0318a3b02a95b32c5006a7f7fa.gz

>>>>

\section{Computation details}

\subsection{Binary image moments}

\subsection{Roundness}

The computation works with any image dimension, and so use the definition
of volume and area of an hypersphere in any dimension.

\begin{eqnarray}
V_n(r) & = {\pi^\frac{n}{2}r^n\over\Gamma(\frac{n}{2} + 1)}
\end{eqnarray}
where $V_n$ is the volume of the hypersphere $n$ is the image dimension,
and $r$ is the radius of the hypersphere.

\begin{eqnarray}
\Gamma\left(\frac{n}{2}+1\right) = \begin{cases}
  \left(\frac{n}{2}\right)!               & \text{if $n$ is even}, \\
  \sqrt{\pi}\frac{n!!}{2^{(n+1)/2}} & \text{if $n$ is odd}.
                                   \end{cases}
\end{eqnarray}

$n!!$ is the double factorial, defined as

\begin{eqnarray}
n!! = \begin{cases}
  1          & \text{if $n < 2$}, \\
  n (n-2)!!  & \text{if $n \geq 2$}.
      \end{cases}
\end{eqnarray}

\begin{eqnarray}
A_n(r) & = {\frac{n V_n}{r}}
\end{eqnarray}

Where $A_n$ is the area of the hypersphere.

\begin{eqnarray}
R & = {\frac{a}{A_n(r)}}
\end{eqnarray}

where $R$ is the roundness, $a$ is the measured area of the object, and the $r$ is the radius of an hypersphere with the same volume than the object.
